### 2014-03-19 paper/designspace.tex
moar pdf figures
some introduction rework started, more detailed explanations of example objects, addition of discussion about gate-based tubes

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/tubespace.png}
\caption{The design space of tubes.  Tube types, media, topologies, and design are discussed more fully in the text.}
\label{fig:tubespace}
\end{figure}

@@

\begin{figure*}[t]
\centering
    \includegraphics[width=\textwidth]{figures/designspace.png}
\caption{The design space of tube-based interactions.  Existing systems are written in regular font.  Those created with fabrication are in {\color{blue}blue}. In \emph{{\color{red}red italic}} are unexplored interactions creatable with custom-fabricated tubes.}
\label{fig:designspace}
\end{figure*}

@@

\emph{Visual} outputs can be mediated by gases, liquids, solid, particulates, or threadables.  EL wire can be threaded through custom paths to create neon signs, as in Figure \ref{fig:neon}.  Colored liquids can be mixed and split before exiting an opaque device, or in a transparent device their mixing, splitting, and paths could be used for display.  PneUIs \cite{Yao-pneui} can be fabricated as single parts: the rubberlike material offered by our Objet is inflatable when thin (200\% elongation at break), and a PneUI located at the terminus of a tube could be actuated by a system-side air pump (see Figure \ref{fig:breathe}).  Mechanical motion can be mediated through fluids (a light object which is partially contained in a tube or located at its end could be pushed by the fluid pressure of the tube) or threadables (e.g., muscle wire).  Large particles trapped in tubes visible to the user can be used for, e.g., maze games (see Figure \ref{fig:maze}).  Using techniques like those described by Harrison, et al., in \cite{Harrison-buttons}  \valkyrie{this paragraph seems terrible.  I think all these paragraphs might seem terrible...}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/helmholz.png}
\caption{This box (a) contains an enclosed Helmholz resonator, seen in the cutaway view (b).  This resonator creates a sound when air is blown through the tube at the top, because air compresses at the small neck joint between the chamber and the tube.  \valkyrie{need to get a test print of this that actually works}}
\label{fig:ocarina}
\end{figure}

>>>>

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/tubespace.pdf}
\caption{The design space of tubes.  Tube types, media, topologies, and design are discussed more fully in the text.}
\label{fig:tubespace}
\end{figure}

@@

\begin{figure*}[t]
\centering
    \includegraphics[width=\textwidth]{figures/designspace.pdf}
\caption{The design space of tube-based interactions.  Existing systems are written in regular font.  Those created with fabrication are in {\color{blue}blue}. In \emph{{\color{red}red italic}} are unexplored interactions creatable with custom-fabricated tubes.}
\label{fig:designspace}
\end{figure*}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/direct.jpg}
\caption{By attaching a servo to a gate structure, it is possible to direct fluid through that tube.  The gate not only has binary positions (a) and (b), but can direct fractional flow, as well (c).  This could be used to create logic gates, as in (d).  These could be used, for example, in science exhibits.}
\label{fig:direct}
\end{figure}

\emph{Visual} outputs can be mediated by gases, liquids, solid, particulates, or threadables.  EL wire can be threaded through custom paths to create neon signs, as in Figure \ref{fig:neon}.  Colored liquids can be mixed and split before exiting an opaque device, or in a transparent device their mixing, splitting, and paths could be used for display.  PneUIs \cite{Yao-pneui} can be fabricated as single parts: the rubberlike material offered by our Objet is inflatable when thin (200\% elongation at break), and a PneUI located at the terminus of a tube could be actuated by a system-side air pump (see Figure \ref{fig:breathe}).  Mechanical motion can be mediated through fluids (a light object which is partially contained in a tube or located at its end could be pushed by the fluid pressure of the tube) or threadables (e.g., muscle wire).  Large particles trapped in tubes visible to the user can be used for, e.g., maze games (see Figure \ref{fig:maze}).  We can even direct fluids through a tube network using a servo-controlled gate, as in Figure \ref{fig:direct}.  Using techniques like those described by Harrison, et al., in \cite{Harrison-buttons}  \valkyrie{this paragraph seems terrible.  I think all these paragraphs might seem terrible...}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/helmholz.jpg}
\caption{This box (a) contains an enclosed Helmholz resonator, seen in the cutaway view (b).  This resonator creates a sound when air is blown through the tube at the top, because air compresses at the small neck joint between the chamber and the tube.  \valkyrie{need to get a test print of this that actually works}}
\label{fig:ocarina}
\end{figure}

### 2014-03-19 paper/exampleobjects.tex
some introduction rework started, more detailed explanations of example objects, addition of discussion about gate-based tubes

Totally tubular examples.  We are making

@@

We created a set of touch-sensitive toys and a companion app, reminiscent of the boat application in \cite{Harrison-acoustic}.  The brain, rabbit, and boat each have several distinct touch points on their surfaces.  These touch points are connected by an interior star topology of tubes filled with conductive copper paint, and touch sensing is performed via a single wire and SFCS (see Figure \ref{fig:toys}).  We built a smart base which can distinguish between the toys and also determine which toy is mounted: since each toy and each gesture has a distinct capacitive signature, we use a simple classifier trained to detect both toy and gesture based on profile.  These devices were all fabricated on a Makerbot Replicator 2.

@@

A custom radio built using tubes allows users to tune to different stations and listen in.  This device uses a network of disconnected open tubes filled with conductive paint to connect traditional electronic components (two potentiometers, a speaker, and an LED) to a microcontroller.  We hid the microcontroller and a battery-driven power supply in the base of the radio to make it portable.  We fabricated this device on our Makerbot Replicator 2.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/pens.jpg}
\caption{This pen holder uses the FlyEye technique to sense the presence or absence of an object in each of its tubes.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:pens}
\end{figure}

Our presence-aware pen holder can distinguish which tool or tools a user has picked up (see Figure \ref{fig:pens}).  Such information was used by \cite{Mueller-constructable} to determine which physical laser pointer a designer was using to interact with their interface.  Our pen holder uses the FlyEye technique described by Wimmer in \cite{Wimmer-flyeye} and contains open tubes filled with fiber optic cables, two per pen chamber.  One tube from each chamber leads to an infrared LED, and the other leads to a camera.  When a pen is in its appointed place, light from the LED is reflected off its bottom and travels through the other optical fiber into the camera, where it registers as a bright point.  A dark point on the camera region appears when a pen has been removed from its place, and the position of the point indicates which pen it is.  This prototype was built by our Objet Connex 260.

@@

Neon art, perhaps best known for its association with Las Vegas, is traditionally made from hand-formed glass tubes containing neon gas.  The tubes light up when a current is passed through them.  For this type of art, the path of the tubes is of crucial importance, as it determines how the sign will look.  We designed a custom neon sign bearing the UIST logo and the waves of Hawaii.  The piece features open tubes due to support-flushing constraints, however the tubes could also be semi-closed.  They have been threaded with EL wire which is lit in sequence to create an animation.  Our sign was fabricated on the Objet Connex 260.

>>>>

To evaluate our tool's capabilities and to explore new points in the design space, we fabricated a set of five prototype objects designed using the tool.

@@

We created a set of touch-sensitive toys and a companion app, reminiscent of the boat application in \cite{Harrison-acoustic}.  The brain, rabbit, and boat each have several distinct touch points on their surfaces.  These touch points are connected by an interior star topology of tubes filled with conductive copper paint, and touch sensing is performed via a single wire and SFCS (see Figure \ref{fig:toys}).  We built a smart base which can distinguish between the toys and also determine which toy is mounted: since each toy and each gesture has a distinct capacitive signature, we use a simple classifier trained to detect both toy and gesture based on profile.  All components were fabricated on a Makerbot Replicator 2.

@@

A custom radio built using tubes allows users to tune to different stations and listen in.  This device uses a network of disconnected open tubes filled with conductive paint to connect traditional electronic components (two potentiometers and a speaker) to a microcontroller (in our case, an Arduino).  We hid the microcontroller and a battery-driven power supply in the base of the radio to make it portable.  For the radio functionality, we attached an Si4703 to the Arduino.  We fabricated this device on our Makerbot Replicator 2.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/pens.jpg}
\caption{This pen holder a modified FlyEye technique to sense the presence or absence of an object in each of its tubes.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:pens}
\end{figure}

Our presence-aware pen holder can distinguish which tool or tools a user has picked up (see Figure \ref{fig:pens}).  Such information was used by \cite{Mueller-constructable} to determine which physical laser pointer a designer was using to interact with their interface.  Our pen holder uses a modification of the FlyEye technique described by Wimmer in \cite{Wimmer-flyeye} and contains open tubes filled with fiber optic cables, one per pen chamber.  Our modification of using a single cable per chamber is possible because we use 6mm diameter fiber optic cables, in comparison to the angel hair tubes used in the original work, and can thus send and receive through the same cable.  At the base of each tube is a QRE1113 line sensor digital breakout board, which has an integrated IR emitter and receiver.   When a pen is in its appointed place, the emitted infrared light is reflected off its bottom and travels back to the receiver, where it registers as bright.  This prototype was built by our Objet Connex 260. \valkyrie{this whole paragraph is unclear}

@@

Neon art, perhaps best known for its association with Las Vegas, is traditionally made from hand-formed glass tubes containing neon gas.  The tubes light up when a current is passed through them.  For this type of art, the path of the tubes is of crucial importance, as it determines how the sign will look.  We designed a custom neon sign bearing the UIST logo and the waves of Hawaii.  The piece features open tubes due to support-flushing constraints, however the tubes could also be semi-closed (one end must remain open to connect the EL wire to its power source).  They have been threaded with EL wire which is lit in sequence to create an animation.  Our sign was fabricated on the Objet Connex 260.

### 2014-03-19 paper/introduction.tex
some introduction rework started, more detailed explanations of example objects, addition of discussion about gate-based tubes

\bjoern{I liked the first sentence of the older intro: ``Makers, as well as professional designers, leverage 3D printers as tools for design work.  A wide array of objects, ranging from bicycle helmets to jewelry to video game controllers, are now prototyped or even manufactured using these machines.  However, most devices fabricated by 3D printers are passive.''}

>>>>

Makers, as well as professional designers, leverage 3D printers as tools for design work.  A wide array of objects, ranging from bicycle helmets to jewelry to video game controllers, are now prototyped or even manufactured using these machines.  However, most devices fabricated by 3D printers are passive.  The major challenge in creating interactive devices using 3D printing technology is the fundamental limitation that these machines cannot fabricate electronics in-place alongside plastic casings.  This forces makers to link their printable designs with the form factor of the off-the-shelf electronics they will insert post-print, rather than giving them the freedom to create interactive components of the size, shape, and type they desire.

Tools, for example Enclosed \cite{Weichel-enclosed}, have been developed to ease this integration step.  However, there remains an elementary gap between the

### 2014-03-19 paper/tubes.tex
add in placeholder figures that are less awful
some introduction rework started, more detailed explanations of example objects, addition of discussion about gate-based tubes

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/exterior.png}
\caption{An example mesh with exterior connection points brushed (a), and the initial A* routing generated (b).  Our physics-based, energy-minimizing rod/tube at rest (c) and after simulation (d).}
\label{fig:tool-process-exterior}
\end{figure}

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/interior.png}
\caption{An input vector graphics file with the points which cannot be tubed as drawn highlighted in {\color{blue}blue} (a).  The connected graph created by our software (b) and the resulting Euler circuit (c) permit creation of a novel neon sign (d).}
\label{fig:tool-process-interior}
\end{figure}

The interior path routing problem is a version of the Chinese Postman Problem\footnote{The CPP is also known as the route inspection problem: \url{http://en.wikipedia.org/wiki/Route_inspection_problem}}, in which we wish to traverse all edges of the graph described in the user's input with a single Euler circuit, much as a postman needs to walk along every road at least once to deliver mail.  We call our relaxation the Spiderman Postman Problem: we allow the creation of non-existing paths (i.e., the postman may traverse buildings in addition to roads).  If inputted path components are disconnected, we must create edges that connect them; additionally we can create new edges connecting odd-degree vertices rather than simply retracing existing edges.  In the final artifact, all created edges will be blocked out by dark material so the inserted medium is not visible (see Figure \ref{fig:tool-process-interior}).

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/intersection-templates.png}
\caption{When edges intersect in the plane (a), we match them to the nearest of our several intersection templates (b) to create 3D paths that do not interfere with each other.}
\label{fig:templates}
\end{figure}

@@

>>>>

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/exterior.jpg}
\caption{An example mesh with exterior connection points selected.  The initial A* routing is drawn in {\color{red}red}, and in {\color{tovi}green} is our physically-based rod after simulation.}
\label{fig:tool-process-exterior}
\end{figure}

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/interior.pdf}
\caption{An input vector graphics file with the points which cannot be tubed as drawn highlighted in {\color{blue}blue} (a).  The connected graph created by our software (b) and the resulting Euler circuit (c) permit creation of a novel neon sign (d).}
\label{fig:tool-process-interior}
\end{figure}

\subsubsection{Routing}
The interior path routing problem is a version of the Chinese Postman Problem\footnote{The CPP is also known as the route inspection problem: \url{http://en.wikipedia.org/wiki/Route_inspection_problem}}, in which we wish to traverse all edges of the graph described in the user's input with a single Euler circuit, much as a postman needs to walk along every road at least once to deliver mail.  We call our relaxation the Spiderman Postman Problem: we allow the creation of non-existing paths (i.e., the postman may traverse buildings in addition to roads).  If inputted path components are disconnected, we must create edges that connect them; additionally we can create new edges connecting odd-degree vertices rather than simply retracing existing edges.  In the final artifact, all created edges will be blocked out by dark material so the inserted medium is not visible (see Figure \ref{fig:tool-process-interior}).

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/templates.jpg}
\caption{When edges intersect in the plane (a), we match them to the nearest of our several intersection templates (b) to create 3D paths that do not interfere with each other.}
\label{fig:templates}
\end{figure}

@@

\valkyrie{For now, we just let them intersect.  The angel hair EL wire is thin enough that we don't actually care.}
